Multi-Agent Reinforcement Learning in Zombie-Survival Games

### 2020-12-20 paper/paper.tex
update paper

\subsection{Agent Design}

When implementing an RL system there are many important design decisions, some key considerations are:

\begin{itemize}
  \item \emph{Algorithm}: Different algorithms are suited to different tasks. A selected algorithm will need to perform well with the selected action-space, state-space, reward function and environmental dynamics.
  \item \emph{State-space}: The state-space describes how environmental observations are presented to the algorithm. Constructing the correct, relevant abstractions allow an agent to better learn the environment.
  \item \emph{Action-space}: The action-space describes actions available to the agent. The level of abstraction here should be fine enough for precise control, but general enough for a policy to be easily learnable.
  \item \emph{Reward function}: The reward function provides a scalar feedback value (positive or negative) to the agent. Some algorithms can model uncertainty in the reward function \citep{ghavamzadeh2016bayesian}, but most expect a point-estimate rather than a distribution. Crafting a consistent reward function that reflects the exact desires of the designer can be challenging \citep{leike2017ai}. Some algorithms can infer the a reward function from feedback \citep{ng2000algorithms}, but most simply try to maximize the explicit reward given by the function.
\end{itemize}

In our scenarios we implement a simple reward function that creates a zero-sum game, where one agent's loss is another's gain.
Our investigation examines the effect of design choices relating to the state-space and action-space, and how those impact the emergence of policies.

@@

In the \emph{armed} scenario we weren't certain how agents would respond.
Survivors were less effective than expected within the training time at using weapons, likely because we underestimated the complexities of a task achievable by humans (in popular depictions of zombie-survivor scenarios, survivors are adept at shooting).

The competitive behavior we saw between survivors was also a surprise, as we expected the survivors to learn the advantage of cooperation.
On reflection, that expectation was a result of our personal ethical conditioning and our anthropomorphizing the survivors.
A more thorough empirical game theoretic analysis such as performed in \citealp{10.5555/3091125.3091194} would likely help us understand the agent incentives.

>>>>

% \subsection{Agent Design}
% 
% When implementing an RL system there are many important design decisions, some key considerations are:
% 
% \begin{itemize}
%   \item \emph{Algorithm}: Different algorithms are suited to different tasks. A selected algorithm will need to perform well with the selected action-space, state-space, reward function and environmental dynamics.
%   \item \emph{State-space}: The state-space describes how environmental observations are presented to the algorithm. Constructing the correct, relevant abstractions allow an agent to better learn the environment.
%   \item \emph{Action-space}: The action-space describes actions available to the agent. The level of abstraction here should be fine enough for precise control, but general enough for a policy to be easily learnable.
%   \item \emph{Reward function}: The reward function provides a scalar feedback value (positive or negative) to the agent. Some algorithms can model uncertainty in the reward function \citep{ghavamzadeh2016bayesian}, but most expect a point-estimate rather than a distribution. Crafting a consistent reward function that reflects the exact desires of the designer can be challenging \citep{leike2017ai}. Some algorithms can infer the a reward function from feedback \citep{ng2000algorithms}, but most simply try to maximize the explicit reward given by the function.
% \end{itemize}
% 
% In our scenarios we implement a simple reward function that creates a zero-sum game, where one agent's loss is another's gain.
% Our investigation examines the effect of design choices relating to the state-space and action-space, and how those impact the emergence of policies.

@@

In the \emph{armed} scenario we weren't certain how agents would respond.
Survivors were less effective than expected within the training time at using weapons, likely because we underestimated the complexities of a task achievable by humans (in popular depictions of zombie-survivor scenarios, survivors are adept at shooting).
The social dilemma presented warrants further study;
a more thorough empirical game theoretic analysis such as performed in \citealp{10.5555/3091125.3091194} would be an interesting exercise.
